---
title: "Phd Survey Report"

date: "2024-02-1"
output: pdf_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```




```{r import data }
## manually delete the second and third rows (about notes) of the raw data (Automatic generation of column comments by qualtrics)
## manually delete invalid survey observations (1. Respondent opened the survey but did not complete it; 2. survey not completed, although some questions were answered)   
## Manually copy all the text data and paste them in the suitable location of Rmarkdown file to make the exported pdf file more aesthetically pleasing.  
## In the second valid observation to question 8-2, the respondent chose "Not applicable" and we manually assigned a value of 0 to this observation in the raw data.  
setwd("D:/RA/Phd_survey")
data <- read.csv("survey_data_numeric.csv")



```



This is an analysis for the survey among the M.Phil./Ph.D. students of the Department of Economics to better understand their experiences, concerns, and any suggestions they might have regarding the Ph.D. program. These survey and report are important initiatives to help us enhance the overall quality of the program and address any areas of concern.
The survey is divided into 6 sections, which are 1. Academic Experience
; 2. Supervision; 3. Resources; 4. Mental Well-being and Support; 5. Professional Development and Job Market; 6. Feedback and Suggestions. We designed questions in these six aspects and collected data from M.Phil./Ph.D. students of the Department of Economics. Finally, we received a total of 12 valid responses, which we have analysed below.



## Part 1. Academic Experience

The first part of the analysis was the academic experience, where we first used formatted questions to collect and analyse students' level of satisfaction with their academic experience in the Department of Economics, followed by an analysis of their main concerns about their academic performance, and finally their personalised opinions.  
In this section, we begin by categorising academic experience into seven aspects and setting a question for each aspect, where students have six options to choose from, namely: "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree","Not applicable". We assign a value of 1 to "Definitely disagree", 2 to "Mostly disagree" and a value of 5 to "Definitely agree" in order to move from complete disagreement to complete agreement. For "Not applicable",we set value of 0.  
We refined the questions into descriptions of a particular aspect to better serve as labels for the statistical graphs, and these labels are shown below, each corresponding to an original question in the survey:

Course quality: The overall academic quality of the courses offered in the program is good.  
Course quantity: My program offers enough courses in my research field.  
Access to seminars: I have access to a good range of seminars in my research area.  
Access to other faculties: I have frequent opportunities to discuss my research with faculties within my institution (in addition to my supervisor).  
Productive discussions with faculties: I find the interactions with other faculty members useful.  
Access to other students: I have frequent opportunities to discuss my research with other research students.  
Access to other researchers: I have frequent opportunities to discuss my research with researchers outside my institution (e.g., seminar speakers).  



```{r Question1, General information, echo=FALSE  }
## The options for these questions measure the degree of respondent agreement or disagreement, and to show the degree to which respondents agreed with each aspect of the academic experience, I calculated the mean of the answer scores for each aspect and used bar charts to show the differences in the mean scores for the different aspects of the scores.

## In this question, the higher the score for each indicator, the higher the average level of satisfaction across all respondents.

library(ggplot2)

## fill missing value（"Not applicable" answer）as 0 (if needed). This makes the mean calculation independent of missing values, and adding zeros does not change the calculated mean value.

#data$Q1_6[is.na(data$Q1_6)] <- 0
#data$Q1_7[is.na(data$Q1_7)] <- 0

##Simplify question options to words for better display in bar charts

# The overall academic quality of the courses offered in the program is good. - Course quality
# My program offers enough courses in my research field. - Course quantity
# I have access to a good range of seminars in my research area. - Access to seminars
# I have frequent opportunities to discuss my research with faculties within my institution (in addition to my supervisor). - Access to other faculties
# I find the interactions with other faculty members useful. - Productive discussions with faculties
# I have frequent opportunities to discuss my research with other research students. - Access to other students
# I have frequent opportunities to discuss my research with researchers outside my institution (e.g., seminar speakers). -  Access to other researchers


# selected question columns for generating mean value
selected_columns_Q1 <- c("Q1_1", "Q1_2", "Q1_3", "Q1_4", "Q1_5", "Q1_6", "Q1_7")

# calculate mean values
mean_values_Q1 <- colMeans(data[selected_columns_Q1])

category_Q1 <- c("Course quality", "Course quantity", "Access to seminars", "Access to other faculties", "Productive discussions with faculties", "Access to other students", " Access to other researchers")

# bar plot
bar_plot_Q1 <- ggplot() +
  geom_bar(data = data.frame(mean_values_Q1), aes(x=factor(category_Q1,levels = unique(category_Q1)) , y = mean_values_Q1),
           stat = "identity", fill = "steelblue") +
  labs(x = "Academic Experience", y = "Degree of Satisfaction") +
  ggtitle("Figure 1. Academic Experience (Mean Value)")  + theme(axis.text.x = element_text(size = 7, angle = 45, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5))



print(bar_plot_Q1)




```


### Mean Values of Each Dimension of Academic Experience

Figure 1 shows the average level of student satisfaction with seven aspects regarding the academic experience, the higher the score for each indicator, the higher the average level of satisfaction across all respondents. When the mean value is above 3, it means that the overall attitude of the students is satisfactory, if below 3, it means unsatisfactory.  
According to the mean satisfaction scores, the "Productive discussions with faculties" indicator received the highest score of about 4.1, indicating that students are highly satisfied with the discussions they have with faculty members.   
On the other hand, the "Course quantity" indicator received the lowest score of about 2.4, indicating that students are not very satisfied with the number of courses available. This suggests that students desire more course options to meet their academic interests and needs.   
Overall, students were satisfied with their academic experience in most aspects, with only one aspect obviously lower than expected. hile students are able to gain constructive input from their dialogue with faculties, they struggled to gain the breadth and depth of knowledge from the courses offered by the department.   




```{r Question1, Specific answers, echo=FALSE  }

question_columns_Q1 <- c("Q1_1", "Q1_2", "Q1_3", "Q1_4", "Q1_5", "Q1_6", "Q1_7")

title_columns_Q1 <- c("Course quality", "Course quantity", "Access to seminars", "Access to other faculties", "Productive discussions with faculties", "Access to other students", " Access to other researchers")


frequency_Q1 <- lapply(question_columns_Q1, function(column) {
  table(data[[column]])
})

color_mapping <- c("Definitely disagree" = "red", "Mostly disagree" = "green", "Neither agree nor disagree" = "blue", "Mostly agree" = "yellow", "Definitely agree" = "purple")

# barplot
par(mfrow = c(2, 4))  
layout(matrix(c(1, 2, 3, 4, 5, 6, 7, 8), nrow = 2, byrow = TRUE), widths = c(1,1,1,1.5))
main_title_Q1 <- "Figure 2. Academic Experience (Individual Value)"

for (i in 1:length(question_columns_Q1)) {
  values <- names(frequency_Q1[[i]])
  values <- factor(values, levels = 1:5)
  
  # color-label one-to-one correspondence
  color <- color_mapping[values]
  
  
  barplot(frequency_Q1[[i]], 
          main = title_columns_Q1[i], 
          cex.main = 0.8,
          xlab = "Answer",
          ylab = "Frequency", 
          ylim = c(0, max(unlist(frequency_Q1))), 
          col = color,
          names.arg = "",
          )
}
title(main = main_title_Q1, line = -1, outer = TRUE)

plot.new()
legend("center", 
       legend = names(color_mapping), 
       fill = unname(color_mapping), 
       title = "Answer",
cex = 0.9,
)


```


### Individual Values of Each Dimension of Academic Experience

In order to get a concrete picture of each student's specific attitudes towards each question, we further counted the responses to each question and showed them in Figure 2.  
For each question, we set five options ("Not applicable" is ignored), which included "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree". For each question, we counted the frequency of occurrence of each option.  
It is evident that students' dissatisfaction is mainly centred on the quantity of the courses. When asked how satisfied they were with "My program offers enough courses in my research field", 4 people responded "Definitely disagree". There were also students who expressed extreme dissatisfaction with the quality of the courses and academic discussions with faculties and other students.  

```{r Question2_separate data, include=FALSE  }


##In qualtrics, responses to multiple choice questions that include more than one option will be recorded in the same cell, which prevents us from counting each response, so it is necessary to assign different responses to different cells before counting them

library(tidyr)

## Assign each response to a different column for multiple choice questions
data <- separate(data, col = "Q2", into = c("Q2_1", "Q2_2", "Q2_3", "Q2_4", "Q2_5", "Q2_6"), sep = ",")


data[is.na(data)] <- 0
```


```{r Question2_analysis, echo=FALSE  }
# selected question columns
selected_columns_Q2 <- c("Q2_1", "Q2_2", "Q2_3", "Q2_4", "Q2_5", "Q2_6")
selected_data_Q2 <- data[, selected_columns_Q2]

# Convert the frequency of responses for each option into a frequency table
selected_matrix_Q2 <- as.matrix(selected_data_Q2)
selected_vector_Q2 <- as.vector(selected_matrix_Q2)
selected_vector_Q2 <- selected_vector_Q2[selected_vector_Q2 != 0]
frequency_table_Q2 <- table(selected_vector_Q2)

#Create a vector of question options to correspond to the numbers recorded for each answer
x_labels <- c("Lack of resources", "Competition with peers", "Others", "No answer")

#if more choice showed in data, add c = ("Workload, "Relationship with advisors") to xlabels

# bar plot
bar_plot_Q2 <- barplot(frequency_table_Q2, main = " Figure 3. Concerns Affecting Academic Performance", xlab = "Answers", ylab = "Frequency", names.arg = x_labels, cex.names = 0.7, ylim = c(0, 10))


```


### Main concerns about Academic Experience

Figure 3 reflects students' concerns about factors that may affect their academic performance, and we found that lack of resources was the most common concern, and that competition with peers also contributed to students' concerns.  
Some students also chose "Others", We recorded their detailed descriptions of this option and showed them below: 

Living costs in HK are high, which adds financial burden to me, especially 
if I live outside the campus.

There is too much emphasis on theory but not the intuition. I personally think theory and mathematics can be easily accessible by reading books, but the main role of an instructor is to clear out the intuition. Most offered courses are either theory or macro-related as well. The offered empirical courses do not have  high quality. For example, I took labor economics  by professor Xuan. She would appaer very unprepared and would spend time to remember what her slides were meant for. After a few sessions, all students turn their camera off and did not truely participate. I also took applies econometrics with professor Koheil. That could also had emphasis on theory rather than intuition. I personally think we need more applied professors who are willing to entract with phd students (unfortunately, a few applied faculty do not seem to be accessible).


### Other Comments about Academic Experience

We also collect students' personalised comments about their academic experience, and We anonymised this information and show it below:

We have a small department/cohort, which means it nearly impossible to provide enough courses for every field and student. Also, UST is far away from other HK universities, which makes the cost of time/transportation/energy high if I want to make use of the resourses of courses/seminars in other universities. It seems that there is nearly no perfect solution for the problem of limited field courses.

I have noticed that recently our department has started organizing dinners, talks, seminars, and happy hours. Thank you so much for doing so. They are extremely helpful. It breaks the barrier between students and faculty members. 

The courses and seminars are highly concentrated in certain fields.

There is few courses and seminars in applied micro (compared with the other field). Is it possible to add more courses and seminars in the future?









## Part 2. Supervision

The second part of the analysis was the supervision, where we first use formatted questions to collect and analyse students' level of satisfaction with their faculty supervision in the Department of Economics, and then collect their personalised opinions.
In this section, we begin by categorising supervision into seven aspects and setting a question for each aspect, where students have six options to choose from, namely: "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree","Not applicable". We assign a value of 1 to "Definitely disagree", 2 to "Mostly disagree" and a value of 5 to "Definitely agree" in order to move from complete disagreement to complete agreement. For "Not applicable",we set value of 0.  
We refined the questions into descriptions of a particular aspect to better serve as labels for the statistical graphs, and these labels are shown below, each corresponding to an original question in the survey:

Overall satisfaction: Overall, I am satisfied with the supervision from my PhD advisor.  
Skills and subject knowledge: My supervisor has the skills and subject knowledge to support my research.

Regular contact: I have regular contact with my supervisor, appropriate for my needs.  
Accessibility: My supervisor has high accessibility (e.g., availability for meetings, responsiveness to emails).  
Research feedback: My supervisor provides feedback that helps me direct my research activities.  
Development support: My supervisor helps me to identify my training and development needs as a researcher.

Empathetic support: My supervisor shows enough encouragement and understanding to me.  



```{r Question4,General information, echo=FALSE  }
## The options for these questions measure the degree of respondent agreement or disagreement, and to show the degree to which respondents agreed with each aspect of the academic experience, I calculated the mean of the answer scores for each aspect and used bar charts to show the differences in the mean scores for the different aspects of the scores

#library(ggplot2)

## In this question, the higher the score for each indicator, the higher the average level of satisfaction across all respondents.


##Simplify question options to words for better display in bar charts

# Overall, I am satisfied with the supervision from my PhD advisor - Overall satisfaction with supervisor
# My supervisor has the skills and subject knowledge to support my research - Skills and subject knowledge
# I have regular contact with my supervisor, appropriate for my needs - Regular contact
# My supervisor has high accessibility (e.g., availability for meetings, responsiveness to emails) - Accessibility
# My supervisor provides feedback that helps me direct my research activities - Research feedback
# My supervisor helps me to identify my training and development needs as a researcher - Development support
# My supervisor shows enough encouragement and understanding to me -  Empathetic support

# selected question columns for generating mean value
selected_columns_Q4 <- c("Q4_1", "Q4_2", "Q4_3", "Q4_4", "Q4_5", "Q4_6", "Q4_7")

# calculate mean values
mean_values_Q4 <- colMeans(data[selected_columns_Q4])

category_Q4 <- c("Overall satisfaction", "Skills and subject knowledge", "Regular contact", "Accessibility", "Research feedback", "Development support","Empathetic support")

# bar plot
bar_plot_Q4 <- ggplot() +
  geom_bar(data = data.frame(mean_values_Q4), aes(x = factor(category_Q4,levels = unique(category_Q4)), y = mean_values_Q4),
           stat = "identity", fill = "steelblue") +
  labs(x = "Supervision", y = "Degree of Satisfaction") +
  ggtitle("Figure 4. Satisfaction with Supervisor (Mean Value)")  + theme(axis.text.x = element_text(size = 7, angle = 45, hjust = 1)) + theme(plot.title = element_text(hjust = 0.5))



print(bar_plot_Q4)


```


### Mean Values of Each Dimension of Supervision

Figure 4 shows the average level of student satisfaction with seven aspects regarding the supervision,the higher the score for each indicator, the higher the average level of satisfaction across all respondents. When the mean value is above 3, it means that the overall attitude of the students is satisfactory, if below 3, it means unsatisfactory.  
According to the mean satisfaction scores, the "Accessibility" indicator received the highest score of around 4.9, indicating that students are satisfied with the high accessibility of faculty members.   
On the other hand, other indicators have slightly lower scores, but the mean values are all over 4, which means that student satisfaction with these indicators is also very high. In comparison, students would like to see further improvements in the developmental support provided by the supervisors.
Overall, students were satisfied with faculty supervision.  





```{r Question4,Specific answers, echo=FALSE  }

# question_columns
question_columns_Q4 <- c("Q4_1", "Q4_2", "Q4_3", "Q4_4", "Q4_5", "Q4_6", "Q4_7")

title_columns_Q4 <- c("Overall satisfaction", "Skills and subject knowledge", "Regular contact", "Accessibility", "Research feedback", "Development support","Empathetic support")


frequency_Q4 <- lapply(question_columns_Q4, function(column) {
  table(data[[column]])
})

color_mapping <- c("Definitely disagree" = "red", "Mostly disagree" = "green", "Neither agree nor disagree" = "blue", "Mostly agree" = "yellow", "Definitely agree" = "purple")

# barplot
par(mfrow = c(2, 4))  
layout(matrix(c(1, 2, 3, 4, 5, 6, 7, 8), nrow = 2, byrow = TRUE), widths = c(1,1,1,1.5))

main_title_Q4 <- "Figure 5. Satisfaction with Supervisor (Individual Value)"



for (i in 1:length(question_columns_Q4)) {
  values <- names(frequency_Q4[[i]])
  values <- factor(values, levels = 1:5)
  
  color <- color_mapping[values]
  
  barplot(frequency_Q4[[i]], 
          main = title_columns_Q4[i],
          cex.main = 0.8,
          xlab = "Answer",
          ylab = "Frequency", 
          ylim = c(0, max(unlist(frequency_Q4))), 
          col = color,
          names.arg = values)  
}

title(main = main_title_Q4, line = -1, outer = TRUE)

plot.new()
legend("center", 
       legend = names(color_mapping), 
       fill = unname(color_mapping), 
       title = "Answer",
cex = 0.9)



```

### Individual Values of Each Dimension of Supervision

We further counted the responses to each question about supervision.
For each question, we set five options, which included "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree". For each question, we counted the frequency of occurrence of each option.  
In Figure 5, it is evident that students have little to no dissatisfaction with every aspect of the supervision. More students expressed "Definitely agree" for "supervisor has high accessibility". Some students expressed slightly lower levels of satisfaction with the development support from supervisors, but overall, students were mostly satisfied with each of these areas.  
No respondents left personalised comments in this section, so we didn't show anything relevant.




## Part 3. Resources

The third part of the analysis was the resources, where we first use formatted questions to collect and analyse students' level of satisfaction with the resources in the Department of Economics, and then collect their personalised opinions.
In this section, we begin by categorising resources into four aspects and setting a question for each aspect, where students have six options to choose from, namely: "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree","Not applicable". We assign a value of 1 to "Definitely disagree", 2 to "Mostly disagree" and a value of 5 to "Definitely agree" in order to move from complete disagreement to complete agreement. For "Not applicable",we set value of 0.  
We refined the questions into descriptions of a particular aspect to better serve as labels for the statistical graphs, and these labels are shown below, each corresponding to an original question in the survey:

Working space: I have a suitable working space when I am on campus.  
Access to datasets: There is appropriate access to datasets needed to support my research.  
Access to software: There is appropriate access to software needed to support my research.  
Access to online journals and books: There is appropriate access to online journals and books needed to support my research.  

```{r Question6,General information, echo=FALSE  }
## The options for these questions measure the degree of respondent agreement or disagreement, and to show the degree to which respondents agreed with each aspect of the academic experience, I calculated the mean of the answer scores for each aspect and used bar charts to show the differences in the mean scores for the different aspects of the scores

#library(ggplot2)

## In this question, the higher the score for each indicator, the higher the average level of satisfaction across all respondents.


##Simplify question options to words for better display in bar charts

# I have a suitable working space when I am on campus - Working space
# There is appropriate access to datasets needed to support my research - Access to datasets
# There is appropriate access to software needed to support my research - Access to software
# There is appropriate access to online journals and books needed to support my research - Access to online journals and books




# selected question columns for generating mean value
selected_columns_Q6 <- c("Q6_1", "Q6_2", "Q6_3", "Q6_4")

# calculate mean values
mean_values_Q6 <- colMeans(data[selected_columns_Q6])

category_Q6 <- c("Working space", "Access to datasets", "Access to software", "Access to online journals and books")

# bar plot
bar_plot_Q6 <- ggplot() + 
  geom_bar(data = data.frame(mean_values_Q6), aes(x = factor(category_Q6,levels = unique(category_Q6)) , y = mean_values_Q6),
           stat = "identity", fill = "steelblue") +
  labs(x = "Resources", y = "Degree of Satisfaction") +
  ggtitle("Figure 6. Satisfaction with Resources (Mean Value)")  + theme(axis.text.x = element_text(size = 6, angle = 30, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5))



print(bar_plot_Q6)


```



### Mean Values of Each Dimension of Resources

Figure 6 shows the average level of student satisfaction with four aspects regarding the resources, the higher the score for each indicator, the higher the average level of satisfaction across all respondents.When the mean value is above 3, it means that the overall attitude of the students is satisfactory,if below 3, it means unsatisfactory.  
According to the mean satisfaction scores, the "Access to online journals and books" indicator received the highest score of about 4.3, indicating that students can download a wide range of academic resources through their school account.  
On the other hand, the "Access to software" indicator received the lowest score of 3, indicating that students are not very satisfied with the software available. This suggests that students desire more softwares to meet their academic interests and needs.  








```{r Question6,Specific answers, echo=FALSE  }


question_columns_Q6 <- c("Q6_1", "Q6_2", "Q6_3", "Q6_4")

title_columns_Q6 <- c("Working space", "Access to datasets", "Access to software", "Access to online journals and books")


frequency_Q6 <- lapply(question_columns_Q6, function(column) {
  table(data[[column]])
})

color_mapping <- c("Definitely disagree" = "red", "Mostly disagree" = "green", "Neither agree nor disagree" = "blue", "Mostly agree" = "yellow", "Definitely agree" = "purple")

# barplot
par(mfrow = c(2, 4))  
mat <- matrix(c(1, 5, 2, 5, 3, 5, 4, 5),2)
layout(mat, widths = c(1, 1, 1, 1), heights = c(1, 1))

main_title_Q6 <- "Figure 7. Satisfaction with Resources (Individual Value)"


for (i in 1:length(question_columns_Q6)) {
  values <- names(frequency_Q6[[i]])
  values <- factor(values, levels = 1:5)
  
  color <- color_mapping[values]
  
  barplot(frequency_Q6[[i]], 
          main = title_columns_Q6[i],
          cex.main = 0.8,
          xlab = "Answer",
          ylab = "Frequency", 
          ylim = c(0, max(unlist(frequency_Q6))), 
          col = color,
          names.arg = values)  
}

title(main = main_title_Q6, line = -1, outer = TRUE)

plot.new()
legend("center", 
       legend = names(color_mapping), 
       fill = unname(color_mapping), 
       title = "Answer",
cex = 1)


```


### Individual Values of Each Dimension of Resources

We further counted the responses to each question about resources.  
For each question, we set five options, which included "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree". For each question, we counted the frequency of occurrence of each option.  
Figure 7 shows that students have little to no dissatisfaction with most aspect of the resources. More students expressed "Definitely agree" for "There is appropriate access to online journals and books needed to support my research" . Some students expressed lower levels of satisfaction with the access to software and the working space. In addition, there was dissatisfaction expressed by students regarding access to datasets.  


### Other Comments about Resources

We also collect students' personalised comments about resources, and we anonymised this information and show it below:

The office is sometimes noisy since professors will walk in directly 
and talk to their students while others are working.

We do not have the school-funded licenses for softwares like Stata and MATLAB, which seems to be essential for Biz school PhDs.

I recommend our department reserve a room for PhD students for their Zoom meetings. 
Our university failed to provide some important software to us, such as Matlab. Even though around 500 HKD subsidy is available, it is not enough.

## Part 4. Mental Well-being and Support

In this section, we begin by categorising mental well-being and support into six aspects and setting a question for each aspect, where students have six options to choose from, namely: "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree","Not applicable". We assign a value of 1 to "Definitely disagree", 2 to "Mostly disagree" and a value of 5 to "Definitely agree" in order to move from complete disagreement to complete agreement. For "Not applicable",we set value of 0.  
We refined the questions into descriptions of a particular aspect to better serve as labels for the statistical graphs, and these labels are shown below, each corresponding to an original question in the survey:

Overall mental health: Your overall mental health over the past year is good.  
Access to mental health support: There is appropriate access to mental health support when needed.  
Sense of belonging: I feel a sense of belonging at my institution.  
Ample student interaction: There are sufficient opportunities to interact with other postgraduate research students.  
Work-life balance: Overall, my work and life are balanced.   
Financial situation: I am satisfied with my current financial situation.  





```{r Question8,General information, echo=FALSE  }
## The options for these questions measure the degree of respondent agreement or disagreement, and to show the degree to which respondents agreed with each aspect of the academic experience, I calculated the mean of the answer scores for each aspect and used bar charts to show the differences in the mean scores for the different aspects of the scores

#library(ggplot2)

## In this question, the higher the score for each indicator, the higher the average level of satisfaction across all respondents.


##Simplify question options to words for better display in bar charts

# Your overall mental health over the past year is good - Overall mental health
# There is appropriate access to mental health support when needed - Access to mental health support
# I feel a sense of belonging at my institution - Sense of belonging
# There are sufficient opportunities to interact with other postgraduate research students - Ample student interaction
# Overall, my work and life are balanced - Work-life balance
# I am satisfied with my current financial situation - Financial situation

# selected question columns for generating mean value
selected_columns_Q8 <- c("Q8_1", "Q8_2", "Q8_3", "Q8_4", "Q8_5", "Q8_6")



# calculate mean values
mean_values_Q8 <- colMeans(data[selected_columns_Q8])

category_Q8 <- c("Overall mental health", "Access to mental health support", "Sense of belonging", "Ample student interaction", "Work-life balance", "Financial situation")
  
# bar plot
bar_plot_Q8 <- ggplot() +
  geom_bar(data = data.frame(mean_values_Q8), aes(x = factor(category_Q8,levels = unique(category_Q8))
, y = mean_values_Q8),
           stat = "identity", fill = "steelblue") +
  labs(x = "Mental Well-being and Support", y = "Degree of Satisfaction") +
  ggtitle("Figure 8. Satisfaction with Mental Well-being and Support (Mean Value)")  + theme(axis.text.x = element_text(size = 7, angle = 45, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5))



print(bar_plot_Q8)


```

### Mean Values of Each Dimension of Mental Well-being and Support

Figure 8 shows the average level of student satisfaction with four aspects regarding the mental well-being and support, the higher the score for each indicator, the higher the average level of satisfaction across all respondents.When the mean value is above 3, it means that the overall attitude of the students is satisfactory,if below 3, it means unsatisfactory.    
According to the mean satisfaction scores, the "Sense of belonging" and "Work-life balance" indicators received the highest score of 4, indicating that students are more satisfied with these aspects.
On the other hand, the "Finalcial situation" and "Student interaction" indicators received the lower scores, indicating that these aspects need to be noticed. In addition, the students' assessment of their mental state was not favourable. 

```{r Question8,Specific answers, echo=FALSE  }

# question_columns
question_columns_Q8 <- c("Q8_1", "Q8_2", "Q8_3", "Q8_4", "Q8_5", "Q8_6")

title_columns_Q8 <- c("Overall mental health", "Access to mental health support", "Sense of belonging", "Ample student interaction", "Work-life balance", "Financial situation")

frequency_Q8 <- lapply(question_columns_Q8, function(column) {
  table(data[[column]])
})

color_mapping <- c("Definitely disagree" = "red", "Mostly disagree" = "green", "Neither agree nor disagree" = "blue", "Mostly agree" = "yellow", "Definitely agree" = "purple", "Not applicable" = "white")

# barplot
par(mfrow = c(2, 4))  
mat <- matrix(c(1, 2, 3, 4, 5, 6, 7, 7),nrow = 2, ncol = 4, byrow = TRUE)
layout(mat, widths = c(1, 1, 1, 1), heights = c(1, 1))

main_title_Q8 <- "Figure 9. Mental Well-being and Support (Individual Value)"



for (i in 1:length(question_columns_Q8)) {
  values <- names(frequency_Q8[[i]])
  values <- factor(values, levels = 1:5)
  
  color <- color_mapping[values]
  
  barplot(frequency_Q8[[i]], 
          main = title_columns_Q8[i], 
          cex.main = 0.8,
          xlab = "Answer",
          ylab = "Frequency", 
          ylim = c(0, max(unlist(frequency_Q8))), 
          col = color,
          names.arg = "")  
}

title(main = main_title_Q8, line = -1, outer = TRUE)

plot.new()
legend("center", 
       legend = names(color_mapping), 
       fill = unname(color_mapping), 
       title = "Answer",
cex = 1)


```




### Individual Values of Each Dimension of Mental Well-being and Support

We further counted the responses to each question about supervision.
For each question, we set five options, which included "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree". For each question, we counted the frequency of occurrence of each option. We showed results in Figure 9.   
A few students expressed extreme dissatisfaction with their current state of mind, which was mainly reflected in a lack of belonging to the department and a lack of interaction with fellow students. However, at the same time, the majority of students expressed satisfaction with access to mental health support when needed. In addition, a few students expressed concerns about work-life balance and their financial situation.

In addition, some students describe specific mental health challenges they have faced recently:

Could not find a clear research career path and research plan while time flied.

I always hear pessimistic news from my peers about the ECON academic job market, which is increasingly to be more and more competitive. Those lower my confidence and enthusiasm, and increase my anxiety and depression. Besides, senior students/JMCs are excellent and successful in the job market, which boosts my confidence recently, but also gives my some pressure, as I may not do as well as they do, and have negative effects on the department placements in the future.

Stress from the uncertainty about the future.

### Other Comments about Mental Well-being and Support

Finally, we also collect students' personalised comments about mental well-being and support, and We anonymised this information and show it below:

The CPI of campus dinning and living grows much faster than our PGS.


## Part 5. Professional Development and Job Market

In this section, we begin by categorising professional development and job market into six aspects and setting a question for each aspect, where students have six options to choose from, namely: "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree","Not applicable". We assign a value of 1 to "Definitely disagree", 2 to "Mostly disagree" and a value of 5 to "Definitely agree" in order to move from complete disagreement to complete agreement. For "Not applicable",we set value of 0.  
We refined the questions into descriptions of a particular aspect to better serve as labels for the statistical graphs, and these labels are shown below, each corresponding to an original question in the survey:

Career instructions, consultation: My program provides useful career instructions and consultation.  
Career development opportunities: There are many career development opportunities provided by  department/university (e.g., workshops, networking events, job fairs).   
Career preparedness: As a result of my research degree programme I feel well prepared for my future career.   
Project skills: My ability to manage projects has developed during my programme.    
Communication skills: My ability to communicate information effectively to diverse audiences has developed during my programme.   
Contacts or professional networks: I have developed contacts or professional networks during my programme.   


```{r Question11,General information, echo=FALSE  }
## The options for these questions measure the degree of respondent agreement or disagreement, and to show the degree to which respondents agreed with each aspect of the academic experience, I calculated the mean of the answer scores for each aspect and used bar charts to show the differences in the mean scores for the different aspects of the scores

#library(ggplot2)

## In this question, the higher the score for each indicator, the higher the average level of satisfaction across all respondents.


##Simplify question options to words for better display in bar charts

# My program provides useful career instructions and consultation - Career instructions and consultation
# There are many career development opportunities provided by department/university (e.g., workshops, networking events, job fairs) - Career development opportunities
# As a result of my research degree programme I feel well prepared for my future career - Career preparedness
# My ability to manage projects has developed during my programme - 
# My ability to communicate information effectively to diverse audiences has developed during my programme - Communication skills
# I have developed contacts or professional networks during my programme - Contacts or professional networks


# selected question columns for generating mean value
selected_columns_Q11 <- c("Q11_1", "Q11_2", "Q11_3", "Q11_4", "Q11_5", "Q11_6")

# calculate mean values
mean_values_Q11 <- colMeans(data[selected_columns_Q11])
category_Q11 <- c("Career instructions, consultation", "Career development opportunities", "Career preparedness", "Project skills", "Communication skills", "Contacts or professional networks")
# bar plot
bar_plot_Q11 <- ggplot() +
  geom_bar(data = data.frame(mean_values_Q11), aes(x =factor(category_Q11,levels = unique(category_Q11))
, y = mean_values_Q11),
           stat = "identity", fill = "steelblue") +
  labs(x = "Professional Development and Job Market (Mean Value)", y = "Degree of Satisfaction")+ 
  ggtitle("Figure 10.Professional Development and Job Market (Mean Value)")  + theme(axis.text.x = element_text(size = 6, angle = 30, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) 



print(bar_plot_Q11)
```


### Mean Values of Each Dimension of Professional Development and Job Market

Figure 10 shows the average level of student satisfaction with six aspects regarding the professional development and job market,the higher the score for each indicator, the higher the average level of satisfaction across all respondents.When the mean value is above 3, it means that the overall attitude of the students is satisfactory,if below 3, it means unsatisfactory.  
According to the mean satisfaction scores, the "Enhanced project skills" and "Communication skills" indicator received the highest score of about 3.8, indicating that Students are better trained in project management and social skills.  
On the other hand, the "Career preparedness" indicator received the lowest score of about 2.6, indicating that students are not very satisfied with the career service the department provided.   



```{r Question11,Specific answers, echo=FALSE  }

question_columns_Q11 <- c("Q11_1", "Q11_2", "Q11_3", "Q11_4", "Q11_5", "Q11_6")

title_columns_Q11 <- c("Career instructions and consultation", "Career development opportunities", "Career preparedness", "Enhanced project skills", "Communication skills", "Contacts or professional networks")


frequency_Q11 <- lapply(question_columns_Q11, function(column) {
  table(data[[column]])
})

color_mapping <- c("Definitely disagree" = "red", "Mostly disagree" = "green", "Neither agree nor disagree" = "blue", "Mostly agree" = "yellow", "Definitely agree" = "purple")

par(mfrow = c(2, 4))  
mat <- matrix(c(1, 2, 3, 4, 5, 6, 7, 7),nrow = 2, ncol = 4, byrow = TRUE)
layout(mat, widths = c(1, 1, 1, 1), heights = c(1, 1))


main_title_Q11 <- "Figure 11. Professional Development and Job Market (Individual Value)"


for (i in 1:length(question_columns_Q11)) {
  values <- names(frequency_Q11[[i]])
  values <- factor(values, levels = 1:5)
  
  color <- color_mapping[values]
  
  barplot(frequency_Q11[[i]], 
          main = title_columns_Q11[i], 
          cex.main = 0.7,
          xlab = "Answer",
          ylab = "Frequency", 
          ylim = c(0, max(unlist(frequency_Q11))), 
          col = color,
          names.arg = values)  
}
title(main = main_title_Q11, line = -1, outer = TRUE)


plot.new()
legend("center", 
       legend = names(color_mapping), 
       fill = unname(color_mapping), 
       title = "Answer",
cex = 1)


```

### Individual Values of Each Dimension of Professional Development and Job Market


We further counted the responses to each question about supervision.
For each question, we set five options, which included "Definitely disagree", "Mostly disagree", "Neither agree nor disagree", "Mostly agree", "Definitely agree". For each question, we counted the frequency of occurrence of each option.  
In Figure 11, a few students expressed extreme dissatisfaction with aspects about career development. There were also some who felt that the academic network they had developed in the department was lower than expected. Comparatively, most students were satisfied with their project management skills.  


```{r Question12, echo=FALSE , warning=FALSE }
#Q12
##Separating multiple-choice questions

#library(tidyr)

data <- separate(data, col = "Q12", into = c("Q12_1", "Q12_2", "Q12_3", "Q12_4", "Q12_5", "Q12_6"), sep = ",")


data[is.na(data)] <- 0





```


```{r Question12_analysis, echo=FALSE  }
# selected question columns
selected_columns_Q12 <- c("Q12_1", "Q12_2", "Q12_3", "Q12_4", "Q12_5", "Q12_6")
selected_data_Q12 <- data[, selected_columns_Q12]

# Convert the frequency of responses for each option into a frequency table
selected_matrix_Q12 <- as.matrix(selected_data_Q12)
selected_vector_Q12 <- as.vector(selected_matrix_Q12)
selected_vector_Q12 <- selected_vector_Q12[selected_vector_Q12 != 0]
frequency_table_Q12 <- table(selected_vector_Q12)



#Create a vector of question options to correspond to the numbers recorded for each answer
x_labels <- c("Lack of opportunities", "Not clear","Job security", "Work-life balance", "Salary expectations" )

##if needed, add "Others" to x_labels

# bar plot
bar_plot_Q12 <- barplot(frequency_table_Q12, main = "Figure 12. Main Concerns about the Job Market", xlab = "Answers", ylab = "Frequency", names.arg = x_labels, cex.names = 0.6)

```

### Main concerns about Professional Development and Job Market


Figure 12 reflects students' concerns about job market, and we found that work-life balance was the most common concern, and that lack of opportunities and salary also contributed to students' concerns.  
We also asked students about their development plans after graduation and these are shown in Figure 13:



```{r Question13, echo=FALSE, warning=FALSE  }
#Q13
##Separating multiple-choice questions

#library(tidyr)

data <- separate(data, col = "Q13", into = c("Q13_1", "Q13_2", "Q13_3", "Q13_4", "Q13_5", "Q13_6","Q13_7","Q13_8"), sep = ",")


data[is.na(data)] <- 0





```


```{r Question13_analysis, echo=FALSE  }
# selected question columns
selected_columns_Q13 <- c("Q13_1", "Q13_2", "Q13_3", "Q13_4", "Q13_5", "Q13_6", "Q13_7", "Q13_8")
selected_data_Q13 <- data[, selected_columns_Q13]

# Convert the frequency of responses for each option into a frequency table
selected_matrix_Q13 <- as.matrix(selected_data_Q13)
selected_vector_Q13 <- as.vector(selected_matrix_Q13)
selected_vector_Q13 <- selected_vector_Q13[selected_vector_Q13 != 0]
frequency_table_Q13 <- table(selected_vector_Q13)

#Create a vector of question options to correspond to the numbers recorded for each answer
x_labels <- c("Academic career in higher education", "Research career in higher education", "Research career outside higher education","Teaching below higher education","Any other professional career", "Self-employment " )

##if needed, add "Others" to x_labels


color_mapping_Q13 <- c("Academic career in higher education" = "red", "Research career in higher education" = "green", "Research career outside higher education" = "blue", "Teaching below higher education" = "yellow", "Any other professional career" = "purple", "Self-employment" = "pink")

color_Q13 <- c("red", "green","blue","yellow","purple","pink")

# bar plot
bar_plot_Q13 <- barplot(frequency_table_Q13, main = "Figure 13. Future Plan", xlab = "Answers", ylab = "Frequency",ylim = c(0, 12), names.arg = "", cex.names = 0.5,col = color_Q13)
legend("topright", 
       legend = names(color_mapping_Q13), 
       fill = unname(color_mapping_Q13), 
cex = 0.7)

```


### Plans for the future

Figure 13 reflects students' plans after graduation.   
Most students plan to continue pursuing their careers in academia after graduation, while others plan to seek research jobs in industry, and a few plan to continue their careers in other fields, such as teaching track or self-employment.  


We also collect students' descriptions about any career development support or resources that would be helpful to them, and We anonymised this information and show it below:

Overseas job opportunities.

Even though our university organizes many job fairs and career events, almost none of them fit PhD students. Also no useful instruction from the career consultation of our university. Hope more job opportunities not only in academia but also in the private sector can be introduced.



## Part 6. Feedback and Suggestions


Finally, we collected feedback and suggestions from students, which we anonymised and presented in full.


### Suggestions

Below are suggestions of students for improving the PhD program in the economics department:

I wish our department can be more internationalized in terms of professor hiring, student placement and event holding. e.g. it would be great if students can have more integrated information about the overseas conference/courses/visiting opportunities.

Hire some applied professors who are willing to entract with phd students. Invite more applied professors for talks and seminars. Focus on the intuition rather than the math.

Hire more senior professors in different research fields. Offer more career consultation and instructions.


### Other Feedback or Comments

Below are feedback or comments that some students would like to share:

I wish our department can be more internationalized in terms of professor hiring, student placement and event holding. e.g. it would be great if students can have more integrated information about the overseas conference/courses/visiting opportunities.

Great department, friendly/supportive environment. I love her.

